???A quantitative framework for investigating the reliability of network construction

### 2017-10-10 manuscript/CI_interactions.tex
saved with UTF-8 encoding to fix a compiling error
added Kate's dotplot of co-occurances vs interactions to the histogram figure, updated caption in text. Some setup to add galler–parasitoid panels later.

  \begin{figure}
    \caption{\textbf{A)} Most pairs of \emph{Salix} and galler species were never observed co-occurring despite the high levels of replication in our example dataset. For those that were observed together at least once, the number of observed co-occurances was generally small (\textless10). Here we show a histogram of the number of pairs of species observed co-occurring at least once. 3986 pairs of species were never observed co-occurring: this is represented by the upwards triangle at 0. \textbf{B)} Most pairs of species that were observed at the same site were never observed interacting. Here we show a histogram of the number of observed interactions within pairs of co-occurring species.}
    \label{histograms}
    \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_histogram.eps}
    \end{figure}

>>>>

  \begin{figure}
    \caption{\textbf{A)} Most pairs of \emph{Salix} and galler species were never observed co-occurring despite the high levels of replication in our example dataset. For those that were observed together at least once, the number of observed co-occurances was generally small (\textless10). Here we show a histogram of the number of pairs of species observed co-occurring at least once. 3986 pairs of species were never observed co-occurring: these pairs are omitted from the histogram. \textbf{B)} Most pairs of species that were observed at the same site were never observed interacting. Here we show a histogram of the number of observed interactions within pairs of co-occurring species. \textbf{C)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurances. Most pairs either are never observed interacting or interact almost every time they co-occur. The red, dashed line indicates a 1:1 relationship between interactions and co-occurances.}
    \label{histograms}
    \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_histogram.eps}
    \end{figure}
